A Hitchhiker's Guide to Reproducible Research in R

### 2021-06-16 manuscript.Rmd
Opening paragraph edits
A few more comments and some edits to show how I think the clarity of the writing can be improved. Comments on the remainder of the manuscript will follow

Increasingly, scientists openly share their data, materials, and analysis code.
Sharing these digital artefacts increases scientific efficiency by enabling researchers to learn from each other, reuse materials, or review published research results, but only if these artifacts are reproducible.
However, making a research project reproducible comes with a variety of challenges, and there is a dire need for reproducibility standards.

This paper has two aims.
First, we want to introduce the reader to a workflow [see @Peikert2019 for details] that ensures reproducibility---defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code. 
The research community has long accepted reproducibility as integral to "good scientific practice" because empirical research hinges on its objectivity meaning "in principle it can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper]
Often, however, projects can not be reproduced by other research teams, despite the best efforts by the creators.
We present four common threats to reproducibility and explain how we can address these with a combination of four solutions from the software engineering community.
Specifically, we demonstrate how the R package `repro` supports researchers in implementing this solution.
The second objective is to present an alternative preregistration scheme that builds upon a reproducible workflow, the so-called preregistration as code (PAC), where the researchers write the complete analysis as code and the bulk of the manuscript, including the sections Introduction, Methods, and Results---initially based on simulated data, before they gather data.

@@

This tutorial aims at researchers who are willing to make all code, data, and materials---publicly or on request---available and should help them ensure the reproducibility of relevant statistical results.
While the willingness to share materials is required for reproducing a project, it is not sufficient.
For example, @hardwicke2018 attempted to reproduce results from open materials in the journal Cognition. 
Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced—--even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and reproduce the results of only 21 articles (within a reasonable time).

These failed attempts to reproduce highlight the need for widely accepted reproducibility standards.
These open repositories do not routinely provide sufficient to reproduce relevant computational and statistical results.
We argue that the research community could benefit more from the increased transparency across scholarly disciplines (that is, data and methods are increasingly openly shared), if more projects could be reproduced.
To increase the proportion of reproducible projects, such reproducibility standard has to balance the trade-off between being rigorous and being easy to use.
A rigorous standard increases the likelihood of any individual project to be actually reproducible.
An easy to use standard, on the other hand, is more likely to be employed across many research projects.
The remainder of this paper is structured along these lines.
The first part introduces theoretical concepts and software solutions that together form a rigorous reproducibility standard.
The second part is a tutorial that shows how these software solutions can be easily employed by researchers with the help of the R package `repro`.

After introducing the conceptual building blocks, this tutorial guides the reader through each step of an open research project, emphasising guaranteeing reproducibility from the very first step on.
We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use an exemplary research question:

>>>>

Increasingly, scientists openly share their data, materials, and analysis code.
Sharing these digital artefacts <!-- consider using the term 'research output' instead, as digital artefacts might be unnecessarily technical-->increases scientific efficiency by enabling researchers to learn from each other, reuse materials, or review published research results, but only if these artifacts are reproducible<!--Does this last statement apply to data and materials? Reproducible materials?-->.
<!-- Suggest adding sentence: The technology is now available to make all artefacts related to a research project available in such a way that the project can be reproduced with minimal effort. --> 
Reproducibility has long been considered integral to empirical research, whose credibility hinges on its objectivity, meaning "in principle it can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper]
In contemporary research, reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
Unfortunately, despite increasing commitment to open science practices, many projects can not yet be reproduced by other research teams.
This is because making a research project reproducible <!-- how does a research project relate to data/materials/code/artefacts?--> comes with a variety of challenges, and there is a dire need for reproducibility standards.

This paper has two aims.
First, we want to introduce the reader to a workflow that ensures reproducibility [see @Peikert2019 for details]. 
<!--Second? This is really a different point than introducing the workflow-->We present four common threats to reproducibility and explain how we can address these with a combination of four solutions from the software engineering community.
<!-- Third? -->Specifically, we demonstrate how the R package `repro` supports researchers in implementing this solution.
<!-- Not sure if this belongs in the present paper. If it does, then I wouldn't introduce it as a separate goal. Instead, I would say something like: The present paper introduces the reader to a workflow that ensures reproducibility by building on several technical solutions originating in the software engineering community. We show how these solutions address several common threats to reproducibility, and enable novel solutions further enhancing the open science workflow, such as 'preregistration as code'.  -->The second objective is to present an alternative preregistration scheme that builds upon a reproducible workflow, the so-called preregistration as code (PAC), where the researchers write the complete analysis as code and the bulk of the manuscript, including the sections Introduction, Methods, and Results---initially based on simulated data, before they gather data.
This tutorial is aimed at researchers who intend to ensure the reproducibility of a research project, and are willing to make relevant code, data, and materials available; whether publicly or on request.

@@

While the willingness to share materials is required for reproducing a project, it is not sufficient.<!-- This sounds like the start of a new paragraph-->
For example, @hardwicke2018 attempted to reproduce results from open materials in the journal Cognition. 
Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced—--even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and reproduce the results of only 21 articles (within a reasonable time).
These failed attempts to reproduce highlight the need for widely accepted reproducibility standards.
The results further illustrate that open repositories do not routinely provide sufficient information to reproduce relevant computational and statistical results.

We argue that the benefits associated with transparency increase if research can additionally be reproduced.
This paper tutorial demonstrates how to make research projects reproducible, while striking a balance between rigor and ease-of-use.
A rigorous standard increases the likelihood of any individual project to be actually reproducible.
An easy to use standard, on the other hand, is more likely to be adopted.
The remainder of this paper is structured along these lines.
The first part introduces theoretical concepts and software solutions that together form a rigorous reproducibility standard.
The second part is a tutorial that shows how these software solutions can be easily employed by researchers with the help of the R package `repro`.

After introducing the conceptual building blocks, this tutorial guides the reader through each step of an open research project, <!--What does this mean? Isn't the whole paper about reproducibility?-->emphasising guaranteeing reproducibility from the very first step on.
We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use an exemplary research question:
